Conformance Checking Using Embeddings and it's Applicability in the Internet of Things

### 2021-12-20 paper.tex
Some final touches

\color{red}
The following paper is structured as follows.
First, some background and important concepts for the rest of the paper are introduced n \cref{sec:background}.
This includes a deeper look at the conformance checking problem, which is given in \cref{sub:conformance}, including a description of the two established families of techniques.
Furthermore, the important limitations of these two approaches are highlighted.
Then a brief overview of the required NLP techniques is given in \cref{sub:nlp}.
Provided with the basic knowledge concerning both conformance checking and NLP, the novel embedding-based conformance checking approaches from \cite{PBWe20} are described in \cref{sec:method}.
After the techniques have been outlined a discussion of the results from their experiments follows in \cref{sec:results}.
\cref{sec:discussion} concludes the paper with a consideration of limitations in their approach and possible future work, as well as a discussion of the applicability of these techniques in the Internet of Things.
\color{black}

\section{Background}
\label{sec:background}
\color{red}
Naturally, there are numerous subproblems to be solved in business process management.
Often each problem can be viewed as a building block in a bigger system, and good solutions to one problem can enable more insightful further analyses in subsequent problems.
For example, the first step in many business process management use cases will be the discovery of a process model.
Once a process model has been obtained through some means further analyses can follow.
One of these fields is conformance checking, which as a technique, closely follows discovery, since its main goal is to quantify how well a model conforms to a log.
There are currently two dominant branches of conformance checking, replay-based algorithms, and trace alignment algorithms.
Peeperkorn et al. present a novel conformance checking technique that follows an alternate route \cite{PBWe20} to address the conformance checking problem, through techniques adapted from natural language processing.
However, before this technique can be discussed in-depth it is paramount to understand some of the basic ideas underlying both conformance checking and natural language processing. 
\color{black}

@@

This is done by keeping track of four numbers: \emph{\underline{p}roduced}, \emph{\underline{c}onsumed}, \emph{\underline{m}issing} and \emph{\underline{r}emaining} tokens during replay.
According to the semantics of Petri nets, whenever a transition is fired it consumes one token from all input places and produces one token in each output place.
However since it is also possible that we are dealing with a non-conformant trace, it can be the case that a trace contains activities, that are not enabled in the model at that point in time.
In this case, a missing token is added to all input places, that did not contain a token, and the $m$ counter is incremented by the according amount.
Conversely, it might also happen, that a trace can be replayed, but that there are stray tokens left in the Petri net after the replay. 
At the end of the replay, the sum of all leftover tokens makes up the $r$ counter.
Both missing and remaining tokens signal deviation from the process model, but both of these numbers are dependent on the length of traces.
The longer a trace is the more activities will be taken, the more tokens will be produced, and the more chances there are for tokens to be missing or remaining.
Importantly a trace where half the produced tokens were never consumed, i.e. remained, should intuitively have lower fitness than one where only a quarter of produced tokens remained.
Of course, the same relationship holds for the other two counters $m$ and $c$.
Then one very naturally arrives at a trace fitness defined as:
\begin{equation}
	fitness(\sigma,N) = \frac{1}{2}(1-\frac{m_{N,\sigma}}{c_{N,\sigma}})+\frac{1}{2}(1-\frac{r_{N,\sigma}}{p_{N,\sigma}})
\end{equation}
, where $x_{N,\sigma}$ is the counter when replaying trace $\sigma$ on Petri net $N$.
Often one does not just want to determine the fitness of one trace but a complete log, then this definition can be extended to 
\begin{equation}
	fitness(L,N) = \frac{1}{2}(1-\frac{\sum_{\sigma\in L}m_{N,\sigma}}{\sum_{\sigma\in L}c_{N,\sigma}})+\frac{1}{2}(1-\frac{\sum_{\sigma\in L}r_{N,\sigma}}{\sum_{\sigma\in L}p_{N,\sigma}})
\end{equation}
Note that log-fitness is not mathematically equivalent to the mean trace fitness.

@@

The second group of popular methods for conformance checking are alignment-based methods.
The goal here is to construct an execution on the model that is as "close" as possible to the observed execution of events in the trace/log.
If a trace is conformant with the model, this is trivially easy, the "closest" execution possible in the model is exactly the observed trace.
In the conformant case, all moves are so-called, synchronous moves, where both the log and the model performed the same event at each step.
However, if a trace is non-conformant, which is, of course, the case that is of interest, then a one-to-one mapping between model and trace is not possible.
To describe that so-called non-synchronous moves are introduced, these describe the case that one of  the model or log performs an activity that does not happen in the other one.
This can be either a move-on-model-only, where the model takes some transition, which was not observed in the log, or it's dual, the move-on-log-only where an event is recorded in the log that is not possible according to the model.
The weighted sum of misalignments can then be used as a cost metric for an alignment. 
The goal is then to construct an optimal alignment between a trace and the model.
It should be obvious that there are infinitely many such alignments, however, we can construct a trace-agnostic alignment, which consists of $n$ moves-on-log-only followed by the shortest path through the model as moves-on-model-only.
This means there is an effective upper limit on the length of alignments that need to be considered, which in turn means that the problem is decidable. 
However, the search space can quickly grow infeasibly large, so heuristics need to be employed to determine optimal alignments in a reasonable time frame.

@@

\color{blue}
Three different techniques were outlined in the focus paper \cite{PBWe20}, all following a similar structure outlined in \cref{fig:structure}.
First, a model log is produced from the model by using appropriate replay semantics for the model.
Then, given these two logs, one real and one produced by replaying the model, it is possible to train the \emph{act2vec} \cite{KBWe18} embedding.
Based on these embeddings a dissimilarity function needs to be defined to compare different traces, however, the \emph{act2vec} embedding only yields distance measurements between activities and not between traces.
Here the differences between the three techniques come into play.
The first two, the Word Mover's Distance \cite{KSKW15} and Iterative Constrained Transfers, can directly utilize the distances between activities to determine a distance between two collections of activities.
The last one, \emph{trace2vec}, further needs to train a trace embedding based on activity embeddings, and can then perform direct comparisons in the trace embedding space.
All three methods however lead to a reasonable dissimilarity metric between traces.
Using one of these metrics a dissimilarity matrix can be built up describing the pairwise dissimilarities between the real log and the model log.
\color{black}
From here on we will assume that each row corresponds to a trace from the model log and each column corresponds to a trace from the real log, i.e. $a_{ij}$ is the dissimilarity of the $i$-th trace from the model log with the $j$-th trace of the real log.
As such, each column contains the dissimilarity of a trace in the real log with all traces from the model log, with the minimum of a column being the closest match in the model log.
A trace that can be closely replayed by the model, i.e. one that has a close match to a trace produced from the model, is a well-fitting one.
As such the column minimum corresponds to a fitness metric of the trace and thus the mean of all column minima is a fitness metric between log and log.
Conversely, each row contains all similarities between a trace in the model log and all traces in the real log.
A precise model should not allow for more traces than observed in the real log, so each model trace should have as close a match as possible in the real log for the model to be precise.
As such the row minimum corresponds to a precision metric for the trace in the model log and thus the mean of all row minima is a precision metric between the logs.

@@

\color{blue}
\begin{algorithm}
	\caption{Word Mover's distance}\label{alg:wmd}
	\begin{algorithmic}
		\State $n:=$ vocabulary size
		\State $p_i,q_i := $ normalized count of activity $i$ in $p$ or $q$ respectively
		\State $c(i,j) :=$ Distance between embeddings of activity $i$ and $j$
		\Function{$F_{WMD}$}{$p,q,c$}
		\State distance $\gets$ $\min \sum_{i,j=1}^n T_{ij}c(i,j)$
		\State subject to:
		\State $\sum_{j=1}^{n}T_{ij}=p_i \forall i \in \{1,...,n\}$ \Comment{Outflow}
		\State $\sum_{i=1}^{n}T_{ij}=q_j \forall j \in \{1,...,n\}$ \Comment{Inflow}
		\State \Return distance
		\EndFunction
	\end{algorithmic}
\end{algorithm}
The Word Mover's Distance \cite{KSKW15} is a variant of the Earth Mover's Distance \cite{RTGu98} adapted for natural language processing.
This family of metrics has proved to be quite robust as well as accurate for a lot of embedding based NLP tasks.
For this reason it was chosen as an initial candidate for the distance function of an embedding based conformance checking technique.
The Earth Mover's distance measures the distance between two probability distributions.
The informal interpretation of this is that there are two distributions, represented by piles of earth.
The distance between two distributions can be interpreted as the amount of work that needs to be done to transform one into the other.
Clearly, the work and thus the distance between two distributions depends on both the amount of earth on each of the piles and on the distance between piles.
Formally the EMD defines a distance metric for probability distributions over some vector space with a notion of distance.

@@

The ICT and ACT again provide a lower bound to the WMD, since it is not guaranteed that the inflow constraint is met, however, the ICT/ACT lower bound is higher than the RWMD lower bound due to the additional constraint that was introduced.
\color{black}
\subsection{trace2vec}
In contrast to the two previous approaches, which used activity embeddings, it is also possible to train trace embeddings.
The relationship between \emph{act2vec} and \emph{trace2vec} is analogous to the one between \emph{word2vec} and \emph{doc2vec}.
When using this method, every trace is embedded into a vector space and any distance metric that is deemed appropriate can be chosen.
In the paper, the cosine similarity \cref{eq:cosine} was chosen for its simplicity and the fact that it is bounded in the interval $[-1,1]$.
\begin{equation}
	\cos(x,  y) = \frac { x \cdot  y}{|| x|| \cdot || y||}
	\label{eq:cosine}
\end{equation}
This is much less computationally expensive than the previous two approaches which were complex distance metrics between two sets of embeddings.

@@

\subsection{Experimental Setup}
\begin{figure}
	\includegraphics[width=1\textwidth]{figures/process-tree}
	\caption{A process tree generated by pm4py using parameters: Min 15, Mode 30, Max 45, sequence 0.75, parallel 0.25. }
	\label{fig:process-tree}
\end{figure}
%To evaluate the suitability of the method three sets of experiments were performed. 
\color{blue}
All experiments utilized (the same) randomly generated process trees, that were constructed using the algorithms in the \emph{pm4py} library.
Three size configurations described by minimum number, the model, and the maximum number of visible activities were chosen: 5-10-15, 10-20-30, and 15-30-45.
Furthermore, four operator configurations were chosen described by the probability for randomly choosing each available operator.
These were in no particular order: Sequence: $0.75$, Parallel $0.25$, secondly Sequence: $0.75$, Choice $0.25$, thirdly 1. Sequence: $0.5$, Parallel $0.25$, Choice $0.25$ and lastly $0.25$ for all (Sequence, Parallel, Choice and Loop) operators.
Both of these configurations were combined to generate a grid of $12$ process trees, with the hope that these cover a sufficient range of different behavior.
An example of such a random process tree is shown in \cref{fig:process-tree}
\footnote{Note that this tree is not the one used by the authors since they did not share their trees or logs, but one generated with the same parameters.}.
\color{black}

@@

The second set of experiments aimed to determine whether the method responded as expected when providing noisy logs.
These experiments were designed to verify the soundness of the approach.
This was done by generating logs from random process trees generated by pm4py, applying random noise on these logs, and determining the conformance between the noiseless and noisy logs.
\color{blue}
Three different types of noise were used: replacing a random activity with another, swapping two random activities, and removing a random activity.
Then,  two noise experiments were performed.
In the first experiment, the percentage of traces that noise was applied to was varied between $10\%$ and $50\%$, but each noise type was applied at most once to each trace.
In the second experiment instead, the percentage of traces to which noise was applied was kept constant at $40\%$, but the number of activities to which noise was applied was varied.
Furthermore, the second experiment only utilized the replacement noise function  omitting the other two.
\color{black}
The expectation is that any reasonable conformance metric should deteriorate the more noise is added to the log.

@@

\color{blue}
\subsection{Scalability Experiment}
\begin{figure}
	\includegraphics[width=1\textwidth]{figures/scaling}
	\caption{Runtimes for all three methods for varying sizes of logs and dictionaries. Data can be found in \cite{MuCa10} Table 2.}
	\label{fig:scalability}
\end{figure}
The first performed experiment aimed to assess the performance  of the three proposed methods.
The experiments were run on an Intel Core i7-9850h, a mid-range consumer CPU.
Experiments were run for all three methods for different sized logs and different sized dictionaries, for embedding based conformance checking algorithms dictionary size is determined by the number of different activities in the log.
All experiments were performed in Python, however, the Word Mover's distance was calculated using pyemd, a Python wrapper to calculate the WMD/EMD with NumPy efficiency.
As such, when comparing ICT and WMD times, the efficiency difference between Python and C should be taken into account.

@@

Lastly, it was considered to design and run another experiment here to evaluate performance and scaling differences between the embedding based approaches and reference approaches like alignments, behavioral fitness and ETC precision, as this is one of the main selling point especially in the IoT and the authors sadly did not include an experiment to that effect.
In light of the complications with the existing experiments and the fact that no evaluation of the reference metrics was included in their code this idea was deemed out of scope for this paper.
\color{black}
\section{Discussion}
\label{sec:discussion}
\subsection{Future Work}
Peeperkorn et al. obtained promising first results for a novel embedding-based approach towards conformance checking.
Yet as the focus was mainly on the introduction and development of a prototype for such an approach there are some natural limitations.
Arguably the biggest limitation were the logs used for the experimental validation.
All used logs were completely synthetic, generated from random process trees.
It is unclear how well the 12 trees used for this resemble real processes and whether these tree configurations are sufficiently representative for the variation exhibited in real life trees\footnote{12 tree configurations were used, 3 sizes and 4 different probability distributions for operations, how strong these vary should be investigated}.
As such it should be a priority to test the proposed methods on real logs, possibly popular benchmark cases, and also to systematically broaden the parameters for random process tree generation to cover more different classes.

\color{blue}
It is also a  prerequisite for further research and possible usage of such methods to convert the distance metrics obtained into proper conformance metrics, especially by restricting values to the interval $[0,1]$.
When that is done further quantitative comparisons between the updated methods and established conformance checking techniques should be performed.
Furthermore, the algorithms used have several parameters which were set as seemingly reasonable standard values.
A thorough investigation into the effect of these parameters should follow since it can not be known whether similar defaults should be used in conformance checking  as in classical NLP problems.
Special attention should be placed on those cases for which the NLP techniques produced perfect values, whereas the others did not.
The methods should be tested with completely perfect and completely imperfect models regarding fitness and precision, as well as nearly perfect and nearly imperfect models to verify that the methods are able to correctly classify both ends of the model spectrum and not misclassify nearly optimal models as perfect.
\color{black}
Apart from that two of the metrics proposed -- WMD and ICT -- do not take the order of words/activities into account.
This is due to the fact that for a lot of NLP problems order is of lesser importance and tasks like document keyword detection can treat a document as an order-less bag of words.
At least from an intuitive understanding of conformance checking, the order of activities is integrally important, and it should at least be investigated if there are significant differences between ordered and orderless approaches with regard to conformance checking.
The authors themselves suggest considering the use of $n$-grams instead of 1-grams, since their application seems more feasible in business processes as compared to classical NLP.

@@

\color{red}
\subsection{Internet of Things}
When analyzing such an approach in the context of the Internet of Things, there are three main facets that need to be considered.
Due to the fact that the Internet of Things itself, as well as it's architectures, are very heterogeneous it will always be possible to find networks where one of the following limitations or requirements does not hold to some extent, however generally speaking the following should be the main considerations when trying to adapt a process management technique to the Internet of Things.
First the Internet of Things is made up of many less powerful machines that generate a lot of data, and while it is of course possible to integrate more powerful computers into the internet of things, high performance, especially on limited hardware, is a major goal.
The second consideration should be that the Internet of Things is very "online", in the sense that Events are constantly produced and thus analysis, such as conformance checking, during process execution is a high desired property of any technique. 
Lastly the Internet of Things is distributed, and as such certain features such as perfect connectivity, knowledge of all members of the network and others are much more relaxed.

@@

Overall it should be noted that online conformance checking is a difficult problem, but that there are certainly possibilities for solutions using the proposed techniques, especially considering their novelty there has been less research how they could be adapted in an online setting, and how such adaptions perform in reality.
There are definitely parallels like word prediction systems for example, where such an approach could prove fruitful in both an online or offline setting.

\subsubsection{Distributed}
\color{black}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{template/splncs04}
\bibliography{literature/bibliography}
%
\end{document}

>>>>

The following paper is structured as follows.
First, some background and important concepts for the rest of the paper are introduced n \cref{sec:background}.
This includes a deeper look at the conformance checking problem, which is given in \cref{sub:conformance}, including a description of the two established families of techniques.
Furthermore, the important limitations of these two approaches are highlighted.
Then a brief overview of the required NLP techniques is given in \cref{sub:nlp}.
Provided with the basic knowledge concerning both conformance checking and NLP, the novel embedding-based conformance checking approaches from \cite{PBWe20} are described in \cref{sec:method}.
After the techniques have been outlined a discussion of the results from their experiments follows in \cref{sec:results}.
\cref{sec:discussion} concludes the paper with a consideration of limitations in their approach and possible future work, as well as a discussion of the applicability of these techniques in the Internet of Things.

\section{Background}
\label{sec:background}

Naturally, there are numerous subproblems to be solved in business process management.
Often each problem can be viewed as a building block in a bigger system, and good solutions to one problem can enable more insightful further analyses in subsequent problems.
For example, the first step in many business process management use cases will be the discovery of a process model.
Once a process model has been obtained through some means further analyses can follow.
One of these fields is conformance checking, which as a technique, closely follows discovery, since its main goal is to quantify how well a model conforms to a log.
There are currently two dominant branches of conformance checking, replay-based algorithms, and trace alignment algorithms.
Peeperkorn et al. present a novel conformance checking technique that follows an alternate route \cite{PBWe20} to address the conformance checking problem, through techniques adapted from natural language processing.
However, before this technique can be discussed in-depth it is paramount to understand some of the basic ideas underlying both conformance checking and natural language processing.

@@

This is done by keeping track of four numbers: \emph{\underline{p}roduced}, \emph{\underline{c}onsumed}, \emph{\underline{m}issing} and \emph{\underline{r}emaining} tokens during replay.
According to the semantics of Petri nets, whenever a transition is fired it consumes one token from all input places and produces one token in each output place.
However since it is also possible that we are dealing with a non-conformant trace, it can be the case that a trace contains activities, that are not enabled in the model at that point in time.
In this case, a missing token is added to all input places, that did not contain a token, and the $m$ counter is incremented by the according amount.
Conversely, it might also happen, that a trace can be replayed, but that there are stray tokens left in the Petri net after the replay. 
At the end of the replay, the sum of all leftover tokens makes up the $r$ counter.
Both missing and remaining tokens signal deviation from the process model, but both of these numbers are dependent on the length of traces.
%The longer a trace is the more activities will be taken, the more tokens will be produced, and the more chances there are for tokens to be missing or remaining.
%Importantly a trace where half the produced tokens were never consumed, i.e. remained, should intuitively have lower fitness than one where only a quarter of produced tokens remained.
%Of course, the same relationship holds for the other two counters $m$ and $c$.
Then one very naturally arrives at a trace fitness defined as:
\begin{equation}
	fitness(\sigma,N) = \frac{1}{2}(1-\frac{m_{N,\sigma}}{c_{N,\sigma}})+\frac{1}{2}(1-\frac{r_{N,\sigma}}{p_{N,\sigma}})
\end{equation}
, where $x_{N,\sigma}$ is the counter when replaying trace $\sigma$ on Petri net $N$.
Often one does not just want to determine the fitness of one trace but a complete log, then this definition can be extended to 
\begin{equation}
	fitness(L,N) = \frac{1}{2}(1-\frac{\sum_{\sigma\in L}m_{N,\sigma}}{\sum_{\sigma\in L}c_{N,\sigma}})+\frac{1}{2}(1-\frac{\sum_{\sigma\in L}r_{N,\sigma}}{\sum_{\sigma\in L}p_{N,\sigma}})
\end{equation}
%Note that log-fitness is not mathematically equivalent to the mean trace fitness.

@@

The second group of popular methods for conformance checking are alignment-based methods.
The goal here is to construct an execution on the model that is as "close" as possible to the observed execution of events in the trace/log.
In the conformant case, all moves are so-called, synchronous moves, where both the log and the model performed the same event at each step.
%However, if a trace is non-conformant, which is, of course, the case that is of interest, then a one-to-one mapping between model and trace is not possible.
In the non-conformant case so-called non-synchronous moves are introduced, these describe the case that one of  the model or log performs an activity that does not happen in the other one.
This can be either a move-on-model-only, where the model takes some transition, which was not observed in the log, or it's dual, the move-on-log-only where an event is recorded in the log that is not possible according to the model.
The weighted sum of misalignments can then be used as a cost metric for an alignment. 
The goal is then to construct an optimal alignment between a trace and the model.
%It should be obvious that there are infinitely many such alignments, however, we can construct a trace-agnostic alignment, which consists of $n$ moves-on-log-only followed by the shortest path through the model as moves-on-model-only.
%This means there is an effective upper limit on the length of alignments that need to be considered, which in turn means that the problem is decidable. 
%However, the search space can quickly grow infeasibly large, so heuristics need to be employed to determine optimal alignments in a reasonable time frame.

@@

Three different techniques were outlined in the focus paper \cite{PBWe20}, all following a similar structure outlined in \cref{fig:structure}.
First, a model log is produced from the model by using appropriate replay semantics for the model.
Then, given these two logs, one real and one produced by replaying the model, it is possible to train the \emph{act2vec} \cite{KBWe18} embedding.
Based on these embeddings a dissimilarity function needs to be defined to compare different traces, however, the \emph{act2vec} embedding only yields distance measurements between activities and not between traces.
Here the differences between the three techniques come into play.
The first two, the Word Mover's Distance \cite{KSKW15} and Iterative Constrained Transfers, can directly utilize the distances between activities to determine a distance between two collections of activities.
The last one, \emph{trace2vec}, further needs to train a trace embedding based on activity embeddings, and can then perform direct comparisons in the trace embedding space.
All three methods however lead to a reasonable dissimilarity metric between traces.
Using one of these metrics a dissimilarity matrix can be built up describing the pairwise dissimilarities between the real log and the model log.

From here on we will assume that each row corresponds to a trace from the model log and each column corresponds to a trace from the real log, i.e. $a_{ij}$ is the dissimilarity of the $i$-th trace from the model log with the $j$-th trace of the real log.
As such, each column contains the dissimilarity of a trace in the real log with all traces from the model log, with the minimum of a column being the closest match in the model log.
A trace that can be closely replayed by the model, i.e. one that has a close match to a trace produced from the model, is a well-fitting one.
As such the column minimum corresponds to a fitness metric of the trace and thus the mean of all column minima is a fitness metric between log and log.
Conversely, each row contains all similarities between a trace in the model log and all traces in the real log.
A precise model should not allow for more traces than observed in the real log, so each model trace should have as close a match as possible in the real log for the model to be precise.
As such the row minimum corresponds to a precision metric for the trace in the model log and thus the mean of all row minima is a precision metric between the logs.

@@

\begin{algorithm}
	\caption{Word Mover's distance}\label{alg:wmd}
	\begin{algorithmic}
		\State $n:=$ vocabulary size
		\State $p_i,q_i := $ normalized count of activity $i$ in $p$ or $q$ respectively
		\State $c(i,j) :=$ Distance between embeddings of activity $i$ and $j$
		\Function{$F_{WMD}$}{$p,q,c$}
		\State distance $\gets$ $\min \sum_{i,j=1}^n T_{ij}c(i,j)$
		\State subject to:
		\State $\sum_{j=1}^{n}T_{ij}=p_i \forall i \in \{1,...,n\}$ \Comment{Outflow}
		\State $\sum_{i=1}^{n}T_{ij}=q_j \forall j \in \{1,...,n\}$ \Comment{Inflow}
		\State \Return distance
		\EndFunction
	\end{algorithmic}
\end{algorithm}
The Word Mover's Distance \cite{KSKW15} is a variant of the Earth Mover's Distance \cite{RTGu98} adapted for natural language processing.
This family of metrics has proved to be quite robust as well as accurate for a lot of embedding based NLP tasks.
For this reason it was chosen as an initial candidate for the distance function of an embedding based conformance checking technique.
The Earth Mover's distance measures the distance between two probability distributions.
The informal interpretation of this is that there are two distributions, represented by piles of earth.
The distance between two distributions can be interpreted as the amount of work that needs to be done to transform one into the other.
Clearly, the work and thus the distance between two distributions depends on both the amount of earth on each of the piles and on the distance between piles.
Formally the EMD defines a distance metric for probability distributions over some vector space with a notion of distance.

@@

The ICT and ACT again provide a lower bound to the WMD, since it is not guaranteed that the inflow constraint is met, however, the ICT/ACT lower bound is higher than the RWMD lower bound due to the additional constraint that was introduced.

\subsection{trace2vec}
In contrast to the two previous approaches, which used activity embeddings, it is also possible to train trace embeddings.
The relationship between \emph{act2vec} and \emph{trace2vec} is analogous to the one between \emph{word2vec} and \emph{doc2vec}.
When using this method, every trace is embedded into a vector space and any distance metric that is deemed appropriate can be chosen.
In the paper, the cosine similarity \cref{eq:cosine} was chosen for its simplicity and the fact that it is bounded in the interval $[-1,1]$.
\begin{equation}
	\cos(x,  y) = \frac { x \cdot  y}{|| x|| \cdot || y||}
	\label{eq:cosine}
\end{equation}
This is much less computationally expensive than the previous two approaches which were complex distance metrics between two sets of embeddings.

@@

\subsection{Experimental Setup}
\begin{figure}
	\includegraphics[width=1\textwidth]{figures/process-tree}
	\caption{A process tree generated by pm4py using parameters: Min 15, Mode 30, Max 45, sequence 0.75, parallel 0.25. }
	\label{fig:process-tree}
\end{figure}
%To evaluate the suitability of the method three sets of experiments were performed.

All experiments utilized (the same) randomly generated process trees, that were constructed using the algorithms in the \emph{pm4py} library.
Three size configurations described by minimum number, the model, and the maximum number of visible activities were chosen: 5-10-15, 10-20-30, and 15-30-45.
Furthermore, four operator configurations were chosen described by the probability for randomly choosing each available operator.
These were in no particular order: Sequence: $0.75$, Parallel $0.25$, secondly Sequence: $0.75$, Choice $0.25$, thirdly 1. Sequence: $0.5$, Parallel $0.25$, Choice $0.25$ and lastly $0.25$ for all (Sequence, Parallel, Choice and Loop) operators.
Both of these configurations were combined to generate a grid of $12$ process trees, with the hope that these cover a sufficient range of different behavior.
An example of such a random process tree is shown in \cref{fig:process-tree}
\footnote{Note that this tree is not the one used by the authors since they did not share their trees or logs, but one generated with the same parameters.}.

@@

The second set of experiments aimed to determine whether the method responded as expected when providing noisy logs.
These experiments were designed to verify the soundness of the approach.
This was done by generating logs from random process trees generated by pm4py, applying random noise on these logs, and determining the conformance between the noiseless and noisy logs.

Three different types of noise were used: replacing a random activity with another, swapping two random activities, and removing a random activity.
Then,  two noise experiments were performed.
In the first experiment, the percentage of traces that noise was applied to was varied between $10\%$ and $50\%$, but each noise type was applied at most once to each trace.
In the second experiment instead, the percentage of traces to which noise was applied was kept constant at $40\%$, but the number of activities to which noise was applied was varied.
Furthermore, the second experiment only utilized the replacement noise function  omitting the other two.

The expectation is that any reasonable conformance metric should deteriorate the more noise is added to the log.

@@

\subsection{Scalability Experiment}
\begin{figure}
	\includegraphics[width=1\textwidth]{figures/scaling}
	\caption{Runtimes for all three methods for varying sizes of logs and dictionaries. Data can be found in \cite{MuCa10} Table 2.}
	\label{fig:scalability}
\end{figure}
The first performed experiment aimed to assess the performance  of the three proposed methods.
The experiments were run on an Intel Core i7-9850h, a mid-range consumer CPU.
Experiments were run for all three methods for different sized logs and different sized dictionaries, for embedding based conformance checking algorithms dictionary size is determined by the number of different activities in the log.
All experiments were performed in Python, however, the Word Mover's distance was calculated using pyemd, a Python wrapper to calculate the WMD/EMD with NumPy efficiency.
As such, when comparing ICT and WMD times, the efficiency difference between Python and C should be taken into account.

@@

Lastly, it was considered to design and run another experiment here to evaluate performance and scaling differences between the embedding based approaches and reference approaches like alignments, behavioral fitness and ETC precision, as this is one of the main selling point especially in the IoT and the authors sadly did not include an experiment to that effect.
In light of the complications with the existing experiments and the fact that no evaluation of the reference metrics was included in their code this idea was deemed out of scope for this paper.

\section{Discussion}
\label{sec:discussion}
\subsection{Future Work}
Peeperkorn et al. obtained promising first results for a novel embedding-based approach towards conformance checking.
Yet as the focus was mainly on the introduction and development of a prototype for such an approach there are some natural limitations.
Arguably the biggest limitation were the logs used for the experimental validation.
All used logs were completely synthetic, generated from random process trees.
It is unclear how well the 12 trees used for this resemble real processes and whether these tree configurations are sufficiently representative for the variation exhibited in real life trees\footnote{12 tree configurations were used, 3 sizes and 4 different probability distributions for operations, how strong these vary should be investigated}.
As such it should be a priority to test the proposed methods on real logs, possibly popular benchmark cases, and also to systematically broaden the parameters for random process tree generation to cover more different classes.

It is also a  prerequisite for further research and possible usage of such methods to convert the distance metrics obtained into proper conformance metrics, especially by restricting values to the interval $[0,1]$.
When that is done further quantitative comparisons between the updated methods and established conformance checking techniques should be performed.
Furthermore, the algorithms used have several parameters which were set as seemingly reasonable standard values.
A thorough investigation into the effect of these parameters should follow since it can not be known whether similar defaults should be used in conformance checking  as in classical NLP problems.
Special attention should be placed on those cases for which the NLP techniques produced perfect values, whereas the others did not.
The methods should be tested with completely perfect and completely imperfect models regarding fitness and precision, as well as nearly perfect and nearly imperfect models to verify that the methods are able to correctly classify both ends of the model spectrum and not misclassify nearly optimal models as perfect.

Apart from that two of the metrics proposed -- WMD and ICT -- do not take the order of words/activities into account.
This is due to the fact that for a lot of NLP problems order is of lesser importance and tasks like document keyword detection can treat a document as an order-less bag of words.
At least from an intuitive understanding of conformance checking, the order of activities is integrally important, and it should at least be investigated if there are significant differences between ordered and orderless approaches with regard to conformance checking.
The authors themselves suggest considering the use of $n$-grams instead of 1-grams, since their application seems more feasible in business processes as compared to classical NLP.

@@

\subsection{Internet of Things}
When analyzing such an approach in the context of the Internet of Things, there are three main facets that need to be considered.
Due to the fact that the Internet of Things itself, as well as it's architectures, are very heterogeneous it will always be possible to find networks where one of the following limitations or requirements does not hold to some extent, however generally speaking the following should be the main considerations when trying to adapt a process management technique to the Internet of Things.
First the Internet of Things generates a lot of data, and the amount of potential data that can be generated is enormous.
This means high performance, for things like real-time analysis, is a major goal.
The second consideration should be that the Internet of Things is very "online", in the sense that events are constantly produced and thus analysis, such as conformance checking, during process execution is a highly desired property of any technique.

@@

Overall it should be noted that online conformance checking is a difficult problem, but that there are certainly possibilities for solutions using the proposed techniques, especially considering their novelty there has been less research how they could be adapted in an online setting, and how such adaptions perform in reality.
But even beyond that there are many potential interesting use cases for embedding based methods in an online method.
For example the use case of predicting the next activity, while outside the bounds of conformance checking, maps very cleanly to word prediction tasks, when using embeddings, so there are certainly very interesting topics in applying embeddings to not only conformance checking  but other process mining tasks as well.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{template/splncs04}
\bibliography{literature/bibliography}
%
\end{document}
